Influence of Connectivity on Dung Beetle Communities

### 2025-06-12 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
small changes and bib

To test for the effects of connectivity on  abundance, species richness, and species diversity we compared the values of the Hill Shannon and Simpson indexes in the different patch types and matrix. For abundance and richness we used generalized linear mixed models (i.e., GLMM) fitted to a poisson distribution  **(bolker citation?)**. Compared (1) the overall species richness and (2) the abundance of the top 6 most common species in each patch type. We included the identity of the sampling block as a random effects. To model our diversity metrics we took a similar approach, but this time using GLMMs with a Gaussian distribution  **(citation)**. All models were fit using `lme4` package  **(citation)**.  Prior to conducting our modeling we evaluated the the suitability of our data with _qqplots_ generated with the `DARMa` package  **(citation)**.

@@

@@

aovM0<-read_csv("./corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```

>>>>

To test for the effects of connectivity on  abundance, species richness, and species diversity we compared the values of the Hill Shannon and Simpson indexes in the different patch types and matrix. For abundance and richness we used generalized linear mixed models (i.e., GLMM) fitted to a poisson distribution  **(bolker citation?)**. Compared (1) the overall species richness and (2) the abundance of the top 6 most common species in each patch type. We included the identity of the sampling block as a random effects. To model our diversity metrics we took a similar approach, but this time using GLMMs with a Gaussian distribution  **(citation)**. All models were fit using `lme4` package  [@bates_fitting_2015].  Prior to conducting our modeling we evaluated the the suitability of our data with _qqplots_ generated with the `DARMa` package  **(citation)**.

@@

```{r, label = shannon, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Dung beetle Shannon diversity in three different --- and the forest matrix surrounding patches.", out.width="50%", fig.align='center'}

knitr::include_graphics("images/sp_shannon_patches.png")

```{r, label = simpson, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Dung beetle Simpson's index in three different --- and the forest matrix surrounding patches.", out.width="50%", fig.align='center'}

knitr::include_graphics("images/sp_simpson_patches.png")

@@

aovM0<-read_csv("~/Rstudio/corridor_beetles/corridor_docs/eric_ms_thesis/tables/aovM0.csv") %>% 
  kable(
      digits = 3,
      align="lcc",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "AOV TABLE CAPTION") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options=c("scale_down","hold_position"),
                font_size = 12,
                position = "center") %>%
  # column_spec(1, italic = T) %>%
  row_spec(0, bold = T)
  # row_spec(1:15, hline_after = T)
aovM0
```
